SVG: The Paper

### 2022-06-09 Analysis/index.Rmd
Figure editing

# some more colours
col3 = c("#d04e00", "#ddc000","#34b6c6",  "#79ad41", "#4063a3")

@@

ggplot(dw, aes(init_weight, fill = method)) + 
  geom_histogram(binwidth = 1/80, position = "identity", alpha = 0.5) +
  geom_vline(xintercept = 1/40, linetype = 2)  -> plt1

dw %>% group_by(observer, method) %>%
  summarise(acc = mean(max_item == 1), .groups = "drop") %>%
  ggplot(aes(y = acc, fill = method)) + geom_boxplot() + 
  geom_hline(yintercept = 1/40, linetype = 2) + 
  scale_y_continuous("Prop. trials first sel. correct") +
  theme(legend.position = "none") -> plt2

>>>>

# some more colours
col3 = c("#d04e00", "#ddc000","#34b6c6",  "#79ad41", "#4063a3")
col2 = c("#d04e00", "#34b6c6")

@@

ggplot(dw, aes(init_weight, fill = method)) + 
  geom_histogram(binwidth = 1/80, position = "identity", alpha = 0.5) +
  geom_vline(xintercept = 1/40, linetype = 2) +
  scale_fill_manual(values = col2)-> plt1

dw %>% group_by(observer, method) %>%
  summarise(acc = mean(max_item == 1), .groups = "drop") %>%
  ggplot(aes(y = acc, fill = method)) + geom_boxplot(alpha = 0.5) + 
  geom_hline(yintercept = 1/40, linetype = 2) + 
  scale_y_continuous("Prop. trials first sel. correct") +
  theme(legend.position = "none") +  
  scale_fill_manual(values = col2) -> plt2
